%-------------------------
% Resume in Latex
% Author: Tianyuan Qiu
% Based off of: https://github.com/jakegut/resume and https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}

\usepackage{xcolor}
\usepackage{soul}
\usepackage{graphicx}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage[default,regular,black]{sourceserifpro}
\usepackage{charter}
% \usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}
{\vspace{8pt}\Large\bfseries\scshape\raggedright \fontfamily{pnc}\selectfont}
{}{0em}{}[\color{gray}\titlerule \vspace{0pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{4pt}}

\newcommand{\grayunderline}[1]{\setulcolor{lightgray}\setul{0.5ex}{0.1pt}\ul{#1}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

% \fancyhead[R]{the top right header}

\begin{center}
    {\Huge \scshape \fontfamily{cmr}\selectfont\textbf{Tianyuan Qiu}} \\ \vspace{14pt}
    \small
    \href{tel:+8618116417218}{\raisebox{-0.1\height}\faPhone\ \grayunderline{+86 181-1641-7218}} ~
    \href{mailto:frank_qiu@sjtu.edu.cn}{\raisebox{-0.15\height}\faEnvelope\ \grayunderline{frankq1024@gmail.com}} ~
    \scalebox{0.93}{\raisebox{-0.05\height}\faEdit}\ Updated: November 2023 ~ \\
    \vspace{4pt}
    \href{https://github.com/PaperL/}{\raisebox{-0.15\height}\faGithub\ \grayunderline{github.com/PaperL}} ~
    \href{https://www.linkedin.com/in/tianyuan-qiu/}{\raisebox{-0.15\height}\faLinkedin\ \grayunderline{linkedin.com/in/tianyuan-qiu}} ~
    \href{https://frankq1024.github.io/}{\raisebox{-0.15\height}\faHome\ \grayunderline{frankq1024.github.io}} ~
    \vspace{-6pt}
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Shanghai Jiao Tong University}{September 2020 -- June 2024}
      {B.S. in Computer Science and Technology (Zhiyuan Honors Program)}{Shanghai, China}
  \resumeSubHeadingListEnd

%------RESEARCH INTEREST-------
\section{Research Interest}
    
My research interest lies in the fields of systems, networking, and machine learning. In particular, I enjoy taking a bottom-up approach, from low level architecture and operating system all the way to the upper layer applications like Machine Learning. Recently, I'm working on improving network performance by offloading with FPGA-based SmartNICs.
\vspace{-4pt}

%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart
    \resumeSubheading
        {\href{https://dsl.cis.upenn.edu/}{\grayunderline{Distributed Systems Laboratory}}, University of Pennsylvania}{August 2023 -- December 2023}
        {Research Assistant, advised by \href{https://vincen.tl/}{\grayunderline{Prof. Vincent Liu}}}{Philadelphia, Pennsylvania, US}
        \resumeItemListStart
            \resumeItem{Investigated co-design of the FPGA-based SmartNIC and the host networking stack.}
            \resumeItem{Leverage idle PCIe transactional bandwidth to mitigate host congestion.}
            \resumeItem{Optimize tail latencies for high-level applications.}
        \resumeItemListEnd

    \resumeSubheading
        {\href{https://bcmi.sjtu.edu.cn/}{\grayunderline{BCMI Laboratory}}, Shanghai Jiao Tong University}{July 2022 -- July 2023}
      {Research Assistant, advised by \href{https://www.ustcnewly.com/}{\grayunderline{Prof. Li Niu}}}{Shanghai, China}
        \resumeItemListStart
            \resumeItem{Proposed a deep learning network of image harmonization guided by reflectance.}
            \resumeItem{Designed a diverse reflectance generation network to predict a variety of plausible foreground reflectances.}
            \resumeItem{Enabled multiple plausible image harmonization results using the outputs from the generation network.}
        \resumeItemListEnd

    \resumeSubheading
        {\href{https://en.zhiyuan.sjtu.edu.cn/}{\grayunderline{Zhiyuan College}}, Shanghai Jiao Tong University}{September 2021 -- June 2023}
        {Teaching Assistant}{Shanghai, China}
        \vspace{7pt}
        \begin{multicols}{2}
            \begin{itemize}[itemsep=0pt, parsep=0pt]
                \item\small CS1953 Programming, Fall 2021
                \item CS1952 Programming Practice, Summer 2022
                \item CS2951 Computer Architecture, Fall 2022
                \item CS2952 Operating System, Spring 2023
            \end{itemize}
        \end{multicols}
    \resumeSubHeadingListEnd
  

%-----------PROJECTS-----------
% \vspace{-25pt}
\section{Selected Projects}
    \vspace{-3pt}
    \small\textcolor{gray}{\textit{(Each project listed was crafted solely by myself and from scratch. Several projects include third-party libraries.)}}
    \vspace{-10pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\href{https://github.com/PaperL/RISC-V_CPU}{\grayunderline{\textbf{RISC-V Out-of-Order Execution CPU}}}
            \enspace$|$\enspace\emph{CPU, FPGA, Verilog, RISC-V}}{Fall 2021}
            \resumeItemListStart
                \resumeItem{Designed an FPGA circuit of a RISC-V (RV32I instruction set) out-of-order execution CPU of Tomasulo algorithm, written in Verilog, tested on AX7035 board.}
            \resumeItemListEnd
            \vspace{-10pt}
        \resumeProjectHeading
            {\href{https://github.com/PaperL/Mxx-Compiler}{\grayunderline{\textbf{Mx* Compiler}}}
            \enspace$|$\enspace\emph{Compiler, LLVM IR, RISC-V, Java}}{Fall 2021}
            \resumeItemListStart
                \resumeItem{Engineered a compiler that compiles a C-and-Java-like language Mx* to LLVM Intermediate Representation and RISC-V assembly (RV32M instruction set), written in Java.}
            \resumeItemListEnd
            \vspace{-10pt}
        \resumeProjectHeading
            {\href{https://github.com/PaperL/Toy_Ray_Tracer}{\grayunderline{\textbf{Ray Tracer}}}
            \enspace$|$\enspace\emph{Ray Tracing, Rust}}{Summer 2021}
            \resumeItemListStart
                \resumeItem{Developed a path tracing renderer featuring textures, BVH, PDF, and other optimizations, written in Rust.}
            \resumeItemListEnd
            % \vspace{-10pt}
            \newpage
        \resumeProjectHeading
            {\href{https://github.com/PaperL/PTL}{\grayunderline{\textbf{PTL}}}
            \enspace$|$\enspace\emph{STL, C++}}{Spring 2021}
            \resumeItemListStart
                \resumeItem{Developed a reimplementation of the C++ Standard Template Library with additional functions.}
            \resumeItemListEnd
            \vspace{-10pt}
        \resumeProjectHeading
            {\href{https://github.com/PaperL/LTL_Model_Checking_Project}{\grayunderline{\textbf{LTL Model Checking}}}
            \enspace$|$\enspace\emph{Model Checking, Logic, Java}}{Spring 2023}
            \resumeItemListStart
                \resumeItem{Implemented a program for reading, parsing, converting, and performing model checking of linear temporal logic formulas, written in Java.}
            \resumeItemListEnd
            \vspace{-10pt}
    \resumeSubHeadingListEnd
\vspace{-4pt}

%-----------Publication---------------
\section{Publication}
    \resumeSubHeadingListStart
    \resumeSubheading
        {Diverse Image Harmonization}{Submitted to CVPR 2024}
        {Xinhao Tao, \textbf{Tianyuan Qiu}, Junyan Cao, Li Niu}{}
    \vspace{10pt}
    \resumeSubheading
        {\href{https://paperl.github.io/Human-3D-Diffusion/}{\grayunderline{DiffAnnot: Improved Neural Annotator with Denoising Diffusion Model}}}{Accepted by ICIPMC 2023}
        {Chaofan Lin, \textbf{Tianyuan Qiu}, Hanchong Yan, Muzi Tao}{}
    \vspace{0pt}
    \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0in, label={}, itemsep=4pt]
\small{
    \item{\textbf{Programming: }{Proficient in algorithm, data structure, modern programming language features (e.g. C/C++, Python, Java, Rust), HDL (e.g. Verilog), database (e.g. MongoDB), utility programs (e.g. MATLAB, Visual Basic, Unity, Processing).}}
    \item{\textbf{Engineering: }{Exceptional code style, document writing, and version control. Proficient in both Windows and Linux environments. Experienced with industry toolchains and documentation (e.g. Xilinx's Vivado).}}
    \item{\textbf{Collaboration and Communication: }{Served as the Class Representative and a member of the Student Union, and the President of the VEX Robotics Club.}}
}
\end{itemize}


%-----------Awards---------------
\section{Awards}
    \resumeSubHeadingListStart
        \resumeProjectHeading{SJTU Merit Scholarship}{2021, 2022}
        \vspace{-17pt}
        \resumeProjectHeading{Zhiyuan Honors Scholarship}{2020, 2021, 2022, 2023}
        \vspace{-17pt}
        \resumeProjectHeading{National Olympiad in Informatics in Provinces, Senior Group, Shanghai Area, First Prize}{2017, 2018}
        \vspace{-17pt}
        \resumeProjectHeading{Asia Open VEX Robotics Competition, VRC High School, First Prize \& Excellence Award (Highest Award)}{2017}
    \resumeSubHeadingListEnd


\end{document}
